Competing Bandits

### 2017-12-05 pres/pres.tex
commit pres + writeup

\item results

>>>>

\item Several things we learned from this experiment:
\item Regardless of the behavioral assumption, Thompson Sampling seems to get a larger market share regardless of what the competing algorithm is.
\item In general, non-adaptive exploration algorithms seem to ``beat'' greedy algorithms.
\item UCB does surprisingly poorly against every algorithm except for StaticGreedy
\item There does not appear to be a large advantage to using an adaptive exploration algorithm compared to a non-adaptive exploration algorithm (as previously noted, Thompson Sampling does slightly better but UCB does worse).
\item The results do not seem to qualitatively vary across different behavioral assumptions.
